### 2023-06-08 bachelorthesis/34-restartscript.tex
#39: Correction Cornelia Lippert

As stated in Chapter \ref{sec:cluster} the \texttt{btrzx1}-cluster has a wall time of 24 hours but since simulations typical run longer than 24 hours one have to restart the simulation after the wall time gets exceeded. Some simulation need even longer so that the simulation itself needs multiple weeks to finish which makes the restart of the simulation a daily task that could be easily forgotten. So to eliminate this minor inconveniences the following restart script were written.

As script language \texttt{python} was chosen because of its easiness to write code and the variety of tools which can interact with the \texttt{bash} shell. \texttt{bash} was also considered but after some issue occurred regarding the mechanism to check wether a file exist or not, \texttt{python} was selected. Furthermore, the script has no requirements because it runs on the standard \texttt{python3} library.

The script was named \texttt{slurm\_monitor.py} to indicate that this script works with the the \texttt{Slurm} resource manager. The source code was pushed to the gkw repository on BitBucket \cite{slurmmonitor} or can be found in Appendix \ref{append:slurmcode}

@@

The restart script has several features which can be used via the command line interface as parser options. The following features with the corresponding parser option were implementing:
\begin{itemize}
    \item \textbf{\textcolor{red}{!Required!}} Set job name not longer than 8 characters to identify simulation\\
          \texttt{-j [JOBNAME], -\/-job-name [JOBNAME]}
    \item Creates jobscript file with defined content\\
          (look into variable \texttt{jobscriptContent} to add more option) \\
          \texttt{-\/-jobscript [JOBSCRIPTFILE]~~~~~~~(default=jobscript-create)}\\
          \texttt{-\/-nodes [NODES]~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=3)}\\
          \texttt{-\/-ntask-per-node [TASKS]~~~~~~~~~~~~~~~~~~~~~~~~(default=32)}\\
          \texttt{-\/-walltime [WALLTIME]~~~~~~(d-hh:mm:ss)~(default=0-24:00:00)}
    \item Start/Restarts simulation until job criteria is suffused\\
          \texttt{-n [TIMESTEPS]~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,\,(default=10000)}\\
          \texttt{-\/-restartfile [RESTARTFILE]~~~~~~~~~~~~~~~~(default=FDS.dat)}
    \item Makes backup after each run before Restart and Restore files after failed run\\
          (uses \texttt{rsync} command line utility)\\
          Quicklinks: local (simulation folder), home (home folder) \\
          \texttt{-b [LOCATION], -\/-backup [LOCATION]~~~~~~~~~~~\,(default=None)}
    \item Reset option after run fails and dump files were written\\
          (rely on \texttt{h5py}, \texttt{pandas} and \texttt{numpy} which get installed by the script itself)\\
          \texttt{-r, -\/-reset~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,(default=False)}
    \item Creates status file with current status and progress bars and updates it dynamically\\
          \texttt{-\/-statusfile [STATUSFILE]~~~~~~~~~~~~~~~(default=status.txt)}
    \item Set form of the output table in status file\\
          Options: fancy (round box), universial (crossplattform), None (No frame)\\
          \texttt{-\/-format [FORMATTABLE]~~~~~~~~~~~~~~~~~~~~~~~~(default=None)}
    \item Sends mail at the beginning, end and restart with status file as attachment\\
          (\texttt{mailx} other equivalent has to be installed, look into \texttt{send\_mail} function for more info)\\
          \texttt{-\/-mail [MAILADDRESS]~~~~~~~~~(mail@server.de)~(default=None)}\\
          \texttt{-\/-restart-mail ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=False)}
    \item Kills monitoring process by using the \texttt{PID} number\\
          \texttt{-\/-kill~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=False)}
    \item Set sleep interval after which the status of the current simulation should be checked\\
          \texttt{-\/-refresh-rate [SLEEPTIME]~~~~~~~~~~~~~~~~~~~~~(default=300)}
    \item Print output of status file table to console\\
          \texttt{-v, -\/-verbose~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,(default=False)}
\end{itemize}
All boolean parameters are switches, i.e., the praser option only changes the value from \texttt{False} to \texttt{True}.

@@

As stated in Chapter \ref{sub:codeFeatures} the restart script is writing a status file with the current status and progress bars of the simulation. The output is formatted like a table and can bei adjust in its appearance with the \texttt{-\/-format} parser option [Chapter \ref{sub:codeFeatures}]. The output types which are written in the status file are listed in Tab. \ref{tab:statusTypes}. To each output prints the restart script the date, time and the duration of the monitoring additionally into the table. 
\begin{center}
    \captionsetup{type=table}
    \begin{tabular}{l | l}
        Type              & Information                                                                                     \\\hline
        \texttt{STARTING} & Start of monitoring process or Start/Restart of simulation                                      \\
        \texttt{CONTINUE} & If the simulation has performed at least one run                                                \\\hline
        \texttt{CONTROL}  & Check of the current time steps of the simulation                                               \\
        \texttt{SUCCESS}  & Stop of monitoring because the time steps condition has been fulfilled                          \\\hline
        \texttt{IMPORT}   & Modules \texttt{h5py}, \texttt{pandas} and \texttt{numpy} will be loaded                        \\
        \texttt{INSTALL}  & Script installs the modules \texttt{h5py}, \texttt{pandas} and \texttt{numpy} on the user level \\
        \texttt{CHECK}    & Required modules to use the reset option are already installed                                  \\\hline
        \texttt{WAITING}  & Simulation is pending in the queue of Slurm                                                     \\
        \texttt{RUNNING}  & Simulation is running on the server                                                             \\\hline
        \texttt{BACKUP}   & The script performs the backup of the data to the predefined location                           \\
        \texttt{RESTORE}  & The script reloads the data from the backup folder if errors occur                              \\
        \texttt{RESET}    & The simulation gets reset with the use of dump files                                            \\\hline 
        \texttt{ERROR}    & During the monitoring does occur an error                                                       \\
                          & Types:                                                                                          \\
                          & No executable (\texttt{gkw.x}), walltime, timeout, no config, \texttt{hdf5}, string error       \\
    \end{tabular}
    \captionof{table}{Output types in status file}
    \label{tab:statusTypes}
\end{center}

To continue, the status file has different style options, e.g., \texttt{fancy}, \texttt{universal} and \texttt{None} which are displayed in Fig. \ref{fig:statusStyle}. 
\begin{center}
\captionsetup{type=figure}
\begin{verbatim}
  ╭───────────────╮    +---------------+    ------------------
  │     fancy     │    |   universal   |           None
  ├───────────────┤    +---------------+    ------------------
  │               │    |               |    
  ╰───────────────╯    +---------------+    ------------------
\end{verbatim}
\captionof{figure}{Styles of output table in status file}
\label{fig:statusStyle}
\end{center}
In addition to that, it writes down the progress of simulation to the end of the status file in form of a progress bar which gets updated dynamically. The progress bar contains the current time step of the simulation in contrast to the required time steps and the progress of the run itself in seconds in relation to the wall time. It also contains the current output from \texttt{squeue}, if the simulation is running or pending, else the important information of the simulation. An example progress bar ist shown in Fig. \ref{fig:statusBar}.
\begin{center}
\captionsetup{type=figure}
\begin{verbatim}
 +------------------------------------------------------------+
 |  JOBID  NAME     USER ST    TIME NODES  NODELIST(REASON)   |
 | 970455 3x1.5 bt712347 CG 3:16:01     3  r03n03,r05n[15-16] |
 +------------------------------------------------------------+
 | PROGRESS  [===================>.....]  ( 80%)  20000/25000 |
 | RUN 13    [===>.....................]  ( 13%)  11462/86400 |
 +------------------------------------------------------------+
\end{verbatim}
\captionof{figure}{Progress bar example}
\label{fig:statusBar}
\end{center}
The progress bar has the advantage that someone can easily access all important information at the glance. To boost productivity the following command could be quite handy:
\begin{lstlisting}
cd $DATA 
find . -name $STATUSFILENAME -exec tail -8 {} \;
\end{lstlisting}
which prints all progress bars of every simulation in the data folder. If one want to see the complete status file change \texttt{tail -8} to \texttt{cat}.
An example status file is displayed in the Appendix \ref{append:status}.

>>>>

As stated in Chapter \ref{sec:cluster} the \texttt{btrzx1}-cluster has a wall time of 24 hours but since simulations typically run longer than 24 hours, the simulation has to be restarted after the wall time is exceeded. Some simulations need multiple weeks making a regular restart vital to obtaining complete sets of simulation data. The following restart script were written to outsource and simplify the process.

As script language \texttt{python} was chosen because of its simple syntax and the variety of tools compatible with the \texttt{bash} shell. \texttt{bash} was also considered, but after some issues occurred regarding the mechanism to check wether a file exist or not, \texttt{python} was selected. Furthermore, the script uses the standard \texttt{python3} library and is therefore executabe with any \texttt{python3} enviroment.

The script was named \texttt{slurm\_monitor.py} to indicate that this script works with the \texttt{Slurm} resource manager. The source code was pushed to the gkw repository on BitBucket \cite{slurmmonitor} or can be found in Appendix \ref{append:slurmcode}

@@

The restart script has several features which can be used via the command line interface as parser options. The following features with the corresponding parser option were implementing:
\begin{itemize}
    \item \textbf{\textcolor{red}{!Required!}} Set job name not longer than 8 characters to identify simulation\\
          \texttt{-j [JOBNAME], -\/-job-name [JOBNAME]}
    \item Can be started from everywhere with simulation folder path\\
          \texttt{-d [DIRECTORY], -\/-dir [DIRECTORY]~~~~~~~~~~~~~(default=cwd)}
    \item Creates jobscript file with defined content (variable \texttt{jobscriptContent})\\
          \texttt{-\/-jobscript [JOBSCRIPTFILE]~~~~~~~(default=jobscript-create)}\\
          \texttt{-\/-nodes [NODES]~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=3)}\\
          \texttt{-\/-ntask-per-node [TASKS]~~~~~~~~~~~~~~~~~~~~~~~~(default=32)}\\
          \texttt{-\/-walltime [WALLTIME]~~~~~~(d-hh:mm:ss)~(default=0-24:00:00)}
    \item Start/Restarts simulation until job criteria is suffused\\
          \texttt{-n [TIMESTEPS]~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,\,(default=10000)}\\
          \texttt{-\/-restartfile [RESTARTFILE]~~~~~~~~~~~~~~~~(default=FDS.dat)}
    \item Makes backup after each run before Restart and Restore files after failed run\\
          Quicklinks: \texttt{local} (simulation folder), \texttt{home} (home folder) \\
          \texttt{-b [LOCATION], -\/-backup [LOCATION]~~~~~~~~~~~\,(default=None)}
    \item Reset option after run fails and dump files were written\\
          (rely on \texttt{h5py}, \texttt{pandas} and \texttt{numpy} which get installed by the script itself)\\
          \texttt{-r, -\/-reset~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,(default=False)}
    \item Creates status file with current status and progress bars and updates it dynamically\\
          \texttt{-\/-statusfile [STATUSFILE]~~~~~~~~~~~~~~~(default=status.txt)}
    \item Set form of the output table in status file\\
          Options: fancy (round box), universial (crossplattform), None (No frame)\\
          \texttt{-\/-format [FORMATTABLE]~~~~~~~~~~~~~~~~~~~~~~~~(default=None)}
    \item Sends mail at the beginning, end and restart with status file as attachment\\
          (\texttt{mailx} other equivalent has to be installed, look into \texttt{send\_mail} function for more info)\\
          \texttt{-\/-mail [MAILADDRESS]~~~~~~~~~(mail@server.de)~(default=None)}\\
          \texttt{-\/-restart-mail ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=False)}
    \item Kills monitoring process by using the \texttt{PID} number\\
          \texttt{-\/-kill~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~(default=False)}
    \item Set sleep interval after which the status of the current simulation should be checked\\
          \texttt{-\/-refresh-rate [SLEEPTIME]~~~~~~~~~~~~~~~~~~~~~(default=300)}
    \item Print output of status file table to console\\
          \texttt{-v, -\/-verbose~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\,(default=False)}
\end{itemize}
All boolean parameters are switches, i.e., the praser option only changes the value from \texttt{False} to \texttt{True}.

@@

As stated in Chapter \ref{sub:codeFeatures} the restart script is writing a status file with the current status and progress bars of the simulation. The output is formatted as a table and can be adjusted in its appearance with the \texttt{-\/-format} parser option [Chapter \ref{sub:codeFeatures}]. The output types written in the status file are listed in Tab. \ref{tab:statusTypes}. To each output the restart script writeesthe date, time and the duration of the monitoring additionally into the table. 
\begin{center}
    \captionsetup{type=table}
    \begin{tabular}{l | l}
        Type              & Information                                                                                     \\\hline
        \texttt{STARTING} & Start monitoring process or Start/Restart of simulation                                         \\
        \texttt{CONTINUE} & If the simulation has performed at least one run                                                \\\hline
        \texttt{CONTROL}  & Check the current time steps of the simulation                                                  \\
        \texttt{SUCCESS}  & Stop monitoring because the time steps condition has been fulfilled                             \\\hline
        \texttt{IMPORT}   & Modules \texttt{h5py}, \texttt{pandas} and \texttt{numpy} will be loaded                        \\
        \texttt{INSTALL}  & Script installs the modules \texttt{h5py}, \texttt{pandas} and \texttt{numpy} on the user level \\
        \texttt{CHECK}    & Required modules to use the reset option are already installed                                  \\\hline
        \texttt{WAITING}  & Simulation is pending in the queue of Slurm                                                     \\
        \texttt{RUNNING}  & Simulation is running on the server                                                             \\\hline
        \texttt{BACKUP}   & The script performs data backup to the predefined location                                      \\
        \texttt{RESTORE}  & The script reloads the data from the backup folder if errors occur                              \\
        \texttt{RESET}    & The simulation restes with the use of dump files                                                \\\hline 
        \texttt{ERROR}    & An error occur during monitoring                                                                \\
                          & Types:                                                                                          \\
                          & No executable (\texttt{gkw.x}), walltime, timeout, no config, \texttt{hdf5}, string error       \\
    \end{tabular}
    \captionof{table}{Output types in status file}
    \label{tab:statusTypes}
\end{center}

To continue, the status file has different style options, e.g., \texttt{fancy}, \texttt{universal} and \texttt{None} which are displayed in Fig. \ref{fig:statusStyle}. 
\begin{center}
\captionsetup{type=figure}
\begin{verbatim}
  ╭───────────────╮    +---------------+    ------------------
  │     fancy     │    |   universal   |           None
  ├───────────────┤    +---------------+    ------------------
  │               │    |               |    
  ╰───────────────╯    +---------------+    ------------------
\end{verbatim}
\captionof{figure}{Styles of output table in status file}
\label{fig:statusStyle}
\end{center}
In addition to that, it dynamically updates the progress of simulation to the end of the status file in form of a progress bar. The progress bar contains the current time step of the simulation in contrast to the required time steps and the progress of the run itself in seconds in relation to the wall time. It also contains the current output from \texttt{squeue}, if the simulation is running or pending, else the important information of the simulation. An example progress bar ist shown in Fig. \ref{fig:statusBar}.
\begin{center}
\captionsetup{type=figure}
\begin{verbatim}
 +------------------------------------------------------------+
 |  JOBID  NAME     USER ST    TIME NODES  NODELIST(REASON)   |
 | 970455 3x1.5 bt712347 CG 3:16:01     3  r03n03,r05n[15-16] |
 +------------------------------------------------------------+
 | PROGRESS  [===================>.....]  ( 80%)  20000/25000 |
 | RUN 13    [===>.....................]  ( 13%)  11462/86400 |
 +------------------------------------------------------------+
\end{verbatim}
\captionof{figure}{Progress bar example}
\label{fig:statusBar}
\end{center}
The progress bar displays all important information at one glance. To boost productivity the following command is recommended:
\begin{lstlisting}
cd $DATA 
find . -name $STATUSFILENAME -exec tail -8 {} \;
\end{lstlisting}
which prints all progress bars of every simulation to the data folder. If one want to see the complete status file change \texttt{tail -8} to \texttt{cat}.
An example status file is displayed in the Appendix \ref{append:status}.

### 2023-06-08 bachelorthesis/41-resolution.tex
#39: Correction Cornelia Lippert

Starting from the \enquote{Standard resolution with 6th order (S6)} [Tab. \ref{tab:resolutionBenchmark}] the first step is to reproduce the result of Ref. \citenum{Peeters2016} in Section IV. Note that, because of selected circular cencentric geometry the used inverse background temperature gradient length is $\rlt = 6.0$ instead of $\rlt = 7.0$ which was used in Section IV of Ref. \citenum{Peeters2016} for $s$-$\alpha$ geometry. In Fig. \ref{fig:eflux-ns16-nvpar64-nmu9} the obtained data is simular to the results from Ref. \citenum{Peeters2016} with subdued turbulence after $\sim 3000\,R/\vth$.

@@

As next step an approach to the finite heat flux threshold were made to verify the selection of the gradient length $\rlt$. As in Ref. \citenum{Peeters2016} in Section V conclude is the finite heat flux threshold approximately located at a grendent length of $\rlt = 6.3$ for circular geometry [FIG. 4 of Ref. \citenum{Peeters2016}]. Therefore following parameters were used
\begin{gather*}
	\rlt \in [6.0, 6.3]~.
\end{gather*}
As seen in Fig. \ref{fig:eflux-gradient-length} for $\rlt = 6.3$ no suppression of turbulence occur in the whole time domain, which is in agreement with Ref. \citenum{Peeters2016}.

@@

In the following the number of grid points for the parallel velocity $\Nvpar$ is reduced to
\begin{gather*}
	\Nvpar \in [16, 32, 48, 64]~.
\end{gather*}
In Fig. \ref{fig:eflux-ns16-nvpar16-32-48-64-nmu9} is clearly visible that the resolution with $\Nvpar = 16$ is not suitable for criteria \textbf{(1)} because here the turbulence is not subdued after a long time period. But resolution $\Nvpar = 32$ is not acceptable as well according to criteria \textbf{(2)} since the surpressed turbulence state gain instability after $\sim 3000\,R/\vth$.\\
So to conclude only grid points with $\Nvpar = 48, 64$ are satisfying the set criteria. Due to criteria \textbf{(1)} the selected resolution will be
\begin{gather*}
	\boxed{\Nvpar = 48}~.
\end{gather*}
With this number of grid points the time till turbulence subdued is halfed compared to the benchmark case, i.e., turbulence suppression occur after $\sim 1500\,R/\vth$.

@@

As next step the number of grid points for the magnetic moment $\Nmu$ were reduced with
\begin{gather*}
	\Nmu \in [6, 9] ~.
\end{gather*}
As in Fig. \ref{fig:eflux-ns16-nvpar64-nmu6-9} shown, the reduction of grid points for the magnetic moment does not significantly impact the suppression of turbulence. The turbulence enters the stationary state in both cases after $\sim 3000\,R/\vth$.

@@

To conclude a curial result the number of grids point for the parallel velocity got reduced to $\Nvpar = 48$ according to Chapter \ref{sub:reduceNvpar}. In this case the turbulence does not subdue for the resolution $\Nmu = 6$ which leads, with the both criteria in mind, to the following resolution
\begin{gather*}
	\boxed{\Nmu = 9}~.
\end{gather*}

@@

In the final step the number of grid points for the magnetic field $\Ns$ get reduced with the following parameters
\begin{gather*}
	\Ns \in [12, 16]~.
\end{gather*}
In Fig. \ref{fig:eflux-ns12-16-nvpar64-nmu9} can be seen that the reduction to $\Ns = 12$ does not satisfy the criteria \textbf{(2)} because the stationary state of the turbulence gets instabil after $\sim 2500\,R/\vth$. This concludes to the following resolution
\begin{gather*}
	\boxed{\Ns = 16}~.
\end{gather*}

@@

Together with the results of Chapter \ref{sub:reduceNvpar}, \ref{sub:reduceNmu} and \ref{sub:reduceNs} the final resolution used in the upcoming simulations are displayed in Tab. \ref{tab:resolution} with reduced number of grid points for the parallel velocity $\Nvpar$.
\begin{center}
	\captionsetup{type=table}
	\begin{tabular}{l | ccccc | ccccc | c | cc}
		& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
		\hline
		S6   & 21    & 83    & 16    & 48                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
	\end{tabular}
	\captionof{table}{
		Resolution used in this paper: Number of toroidal modes $N_m$, number of radial modes $N_x$, number of grid points along the magnetic field $N_s$,number of parallel velocity grid points $N_{\nu_\parallel}$, number of magnetic moment grid points $N_\mu$, dissipation coefficient used in convection along the magnetic field $D$,the velocity in the dissipation scheme $\nu_d$, dissipation coefficient used in the trapping term $D_{\nu_\parallel}$, damping coefficient of radial modes $D_x$, damping coefficient of toroidal modes $D_y$, order of the scheme used for the zonal mode, maximum poloidal wave vector $k_y\rho$, and maximum radial wave vector $k_x\rho$
	}
	\label{tab:resolution}
\end{center}

>>>>

Starting from the \enquote{Standard resolution with 6th order (S6)} [Tab. \ref{tab:resolutionBenchmark}] the first step is to reproduce the result of Ref. \citenum{Peeters2016} in Section IV. Note that, because of selected circular concentric geometry the used inverse background temperature gradient length is $\rlt = 6.0$ instead of $\rlt = 7.0$ which was used in Section IV of Ref. \citenum{Peeters2016} for $s$-$\alpha$ geometry. In Fig. \ref{fig:eflux-ns16-nvpar64-nmu9} the obtained data is simular to the results from Ref. \citenum{Peeters2016} with subdued turbulence after $\sim 3000\,R/\vth$.

@@

As next step to verify the selection of the gradient length $\rlt$ an approach to the finite heat flux threshold was made. As Ref. \citenum{Peeters2016} in Section V concludes the finite heat flux threshold is approximately located at a gradient length of $\rlt = 6.3$ for circular geometry [FIG. 4 of Ref. \citenum{Peeters2016}]. Therefore following parameters were used
\begin{gather*}
	\rlt \in [6.0, 6.3]~.
\end{gather*}
As seen in Fig. \ref{fig:eflux-gradient-length} for $\rlt = 6.3$ no suppression of turbulence occur in the whole time domain, which is in agreement with Ref. \citenum{Peeters2016}.

@@

In the following the number of grid points for the parallel velocity $\Nvpar$ is reduced to
\begin{gather*}
	\Nvpar \in [16, 32, 48, 64]~.
\end{gather*}
In Fig. \ref{fig:eflux-ns16-nvpar16-32-48-64-nmu9} is clearly visible that the resolution with $\Nvpar = 16$ is not suitable for criteria \textbf{(1)} because here the turbulence is not subdued after a long time period. But resolution $\Nvpar = 32$ is not acceptable as well according to criteria \textbf{(2)} since the surpressed turbulence state gain instability after $\sim 3000\,R/\vth$.\\
So to conclude only grid points with $\Nvpar = 48, 64$ are satisfying the set criteria. Due to criteria \textbf{(1)} the selected resolution is
\begin{gather*}
	\boxed{\Nvpar = 48}~.
\end{gather*}
With this number of grid points the time until turbulence subdued is halfed compared to the benchmark case, i.e., turbulence suppression occur after $\sim 1500\,R/\vth$.

@@

In the next step the number of grid points for the magnetic moment $\Nmu$ were reduced with
\begin{gather*}
	\Nmu \in [6, 9] ~.
\end{gather*}
As in Fig. \ref{fig:eflux-ns16-nvpar64-nmu6-9} shown, the reduction of grid points for the magnetic moment does not significantly impact the suppression of turbulence. The turbulence enters the stationary state in both cases after $\sim 3000\,R/\vth$.

@@

To conclude a curial result the number of grid points for the parallel velocity got reduced to $\Nvpar = 48$ according to Chapter \ref{sub:reduceNvpar}. In this case the turbulence does not subdue for the resolution $\Nmu = 6$ which leads, with both criteria in mind, to the following resolution
\begin{gather*}
	\boxed{\Nmu = 9}~.
\end{gather*}

@@

In the final step the number of grid points for the magnetic field $\Ns$ gets reduced with the following parameters
\begin{gather*}
	\Ns \in [12, 16]~.
\end{gather*}
In Fig. \ref{fig:eflux-ns12-16-nvpar64-nmu9} can be seen that the reduction to $\Ns = 12$ does not satisfy the criteria \textbf{(2)} because the stationary state of the turbulence gets instabil after $\sim 2500\,R/\vth$. This concludes to the following resolution
\begin{gather*}
	\boxed{\Ns = 16}~.
\end{gather*}

@@

Together with the results of Chapter \ref{sub:reduceNvpar}, \ref{sub:reduceNmu} and \ref{sub:reduceNs} the final resolution used in the upcoming simulations is displayed in Tab. \ref{tab:resolution}, with reduced number of grid points for the parallel velocity $\Nvpar$.
\begin{center}
	\captionsetup{type=table}
	\begin{tabular}{l | ccccc | ccccc | c | cc}
		& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
		\hline
		S6   & 21    & 83    & 16    & 48                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
	\end{tabular}
	\captionof{table}{
		Resolution used in this paper: Number of toroidal modes $N_m$, number of radial modes $N_x$, number of grid points along the magnetic field $N_s$,number of parallel velocity grid points $N_{\nu_\parallel}$, number of magnetic moment grid points $N_\mu$, dissipation coefficient used in convection along the magnetic field $D$,the velocity in the dissipation scheme $\nu_d$, dissipation coefficient used in the trapping term $D_{\nu_\parallel}$, damping coefficient of radial modes $D_x$, damping coefficient of toroidal modes $D_y$, order of the scheme used for the zonal mode, maximum poloidal wave vector $k_y\rho$, and maximum radial wave vector $k_x\rho$
	}
	\label{tab:resolution}
\end{center}
